---
title: "Copepod analysis"
author: "Sam Bashevkin"
date: "12/9/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages

```{r}
require(tidyverse)
require(zooper)
require(lubridate)
require(brms)
require(spacetools)
require(sf)
require(geoR)
require(corpcor)
```

# Cluster nearby stations

```{r}
Stations<-stations%>%
  mutate(Station=paste(Source, Station))%>%
  filter(Source!="YBFMP")%>%
  drop_na(Latitude, Longitude)

Stations_clust <- Pointcluster(Stations, 1000, Latitude, Longitude, Station, Expand = FALSE)

#plot(Stations$Longitude, Stations$Latitude)
#plot(Stations_clust$Longitude, Stations_clust$Latitude)

Delta_transitioned <- spacetools::Maptransitioner(spacetools::Delta)

#Get in-water distance between stations
distance <- Waterdist(Delta, Stations_clust, Latitude, Longitude, Clust, Water_map_transitioned = Delta_transitioned)

Stations_final <- unnest(Stations_clust, Station)
```

#Load zooplankton data

```{r}
PF<-zoopComb%>%
  filter(Taxname=="Pseudodiaptomus forbesi")%>%
  left_join(zoopEnvComb%>%
              select(-Source),
            by="SampleID")%>%
  filter(Year>1995)%>% # Introduced in 1987, give them 8 years to get established
  mutate(Date_num=as.numeric(Date))%>%
  mutate(SalSurf_l = log(SalSurf),
         Julian_day = yday(Date),
         Count=round(CPUE*Volume))%>%
  mutate_at(vars(Date_num, SalSurf, SalSurf_l, Temperature, Latitude, Longitude), list(s=~(.-mean(., na.rm=T))/sd(., na.rm=T)))%>%
  drop_na(Date, SalSurf, Temperature, Latitude, Longitude, CPUE)%>%
  mutate(Station=paste(Source, Station))%>%
  left_join(Stations_final%>%
              select(Clust, Station),
            by="Station")%>%
  mutate(Clust=as.character(Clust))%>%
  rename(Clustered_station = Clust)%>%
  mutate(Clustered_station2 = Clustered_station)

# Subset distance matrix to just those station clusters present in the dataset

distance<-distance/max(distance)
distance2<-distance[which(rownames(distance)%in%unique(PF$Clustered_station)), which(colnames(distance)%in%unique(PF$Clustered_station))]

distance_cov <-cov.spatial(distance2, cov.pars=c(1,2))
distance_cov <- make.positive.definite(distance_cov)
```

#Exploratory plots

Salinity
```{r}
ggplot(PF, aes(x=log(SalSurf), y=log(CPUE+1)))+
  geom_point(alpha=0.2)+
  scale_y_continuous(expand = expand_scale(mult=c(0.01, 0.05)))+
  scale_x_continuous(expand = expand_scale(mult=c(0.01, 0.05)))+
  facet_wrap(~month(Date))+
  theme_bw()+
  theme(panel.grid=element_blank())
```

Quadratic


Temperature
```{r}
ggplot(PF, aes(x=Temperature, y=log(CPUE+1)))+
  geom_point(alpha=0.2)+
  scale_y_continuous(expand = expand_scale(mult=c(0.01, 0.05)))+
  scale_x_continuous(expand = expand_scale(mult=c(0.01, 0.05)))+
  facet_wrap(~month(Date))+
  theme_bw()+
  theme(panel.grid=element_blank())
```

More in warmer temperatures, even controlling for month

Tide
```{r}
ggplot(PF, aes(x=Tide, y=log(CPUE+1)))+
  geom_boxplot()+
  geom_violin()+
  scale_y_continuous(expand = expand_scale(mult=c(0.01, 0.05)))+
  #scale_x_continuous(expand = expand_scale(mult=c(0.01, 0.05)))+
  theme_bw()+
  theme(panel.grid=element_blank())
```

Not much here

Secchi
```{r}
ggplot(PF, aes(x=Secchi, y=log(CPUE+1)))+
  geom_point(alpha=0.2)+
  scale_y_continuous(expand = expand_scale(mult=c(0.01, 0.05)))+
  scale_x_continuous(expand = expand_scale(mult=c(0.01, 0.05)))+
  facet_wrap(~month(Date))+
  theme_bw()+
  theme(panel.grid=element_blank())
```

Unclear

#Model

```{r}
iterations <- 5e3
warmup <- iterations/4

mbase<-brm(CPUE ~ 1, family=hurdle_gamma(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)
mbase<-add_criterion(mbase, c("loo", "waic"))

mbase2<-brm(CPUE ~ 1, family=hurdle_gamma(link="inverse"),
       data=PF,
       prior=prior(normal(0,100), class="Intercept"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)

mbase3<-brm(CPUE ~ 1, family=hurdle_gamma(link="softplus"),
       data=PF,
       prior=prior(normal(0,100), class="Intercept"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)

mbase4<-brm(CPUE ~ 1, family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)
mbase4<-add_criterion(mbase4, c("loo", "waic"))

mbaseST<-brm(CPUE ~ t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)), family=hurdle_gamma(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)
mbaseST<-add_criterion(mbaseST, c("loo", "waic"), reloo = TRUE)

mbase4ST<-brm(CPUE ~ t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)
mbase4ST<-add_criterion(mbase4ST, c("loo", "waic"))

mbaseST.2<-brm(CPUE ~ t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)), family=hurdle_gamma(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sds"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)
mbaseST.2<-add_criterion(mbaseST.2, c("loo", "waic"))

mbase4ST.2<-brm(CPUE ~ t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma")+
         prior(cauchy(0,5), class="sds"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)
mbase4ST.2<-add_criterion(mbase4ST.2, c("loo", "waic"))

mbaseST2<-brm(CPUE ~ t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, bs="cc"), family=hurdle_gamma(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
mbaseST2<-add_criterion(mbaseST2, c("loo", "waic"))

mbase4ST2<-brm(CPUE ~ t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, bs="cc"), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
mbase4ST2<-add_criterion(mbase4ST2, c("loo", "waic"))

mbase4ST3<-brm(CPUE ~ t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, Year, bs=c("cc", "cr")), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
mbase4ST3<-add_criterion(mbase4ST3, c("loo", "waic"))

mbase4ST4<-brm(CPUE ~ t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, Year, bs=c("cc", "cr")) + (1|Source), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
mbase4ST4<-add_criterion(mbase4ST4, c("loo", "waic"))

mbase4ST5<-brm(CPUE ~ s(Date_num_s) + t2(Julian_day, Year, bs=c("cc", "cr")) + (1|Source) + (1|Clustered_station), family=hurdle_lognormal(),
       data=PF, cov_ranef = list(Clustered_station=distance_cov),
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control = list(max_treedepth = 15))
mbase4ST5<-add_criterion(mbase4ST5, c("loo", "waic"))
save.image("~/SDP/CopModels.RData")

mbase4ST6<-brm(CPUE ~ s(Date_num_s) + t2(Julian_day, Year, bs=c("cc", "cr")) + (1|Source) + (1|Clustered_station) + (1|Clustered_station2), family=hurdle_lognormal(),
       data=PF, cov_ranef = list(Clustered_station=distance_cov),
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control = list(max_treedepth = 15))
mbase4ST6<-add_criterion(mbase4ST6, c("loo", "waic"))

m.1<-brm(CPUE ~ s(SalSurf_s) + s(Temperature_s) + t2(Latitude_s, Longitude_s, Date_num_s), family=hurdle_gamma(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.9))
m.1<-add_criterion(m.1, c("loo", "waic"))

m4.1.1<-brm(CPUE ~ s(SalSurf_l_s) + s(Temperature_s) + t2(Latitude_s, Longitude_s, Date_num_s)+ t2(Julian_day, bs="cc"), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
m4.1.1<-add_criterion(m4.1.1, c("loo", "waic"))

m4.1.2<-brm(CPUE ~ s(SalSurf_l_s) + s(Temperature_s) + t2(Julian_day, bs="cc"), family=hurdle_lognormal(),
       data=PF, autocor = cor_arma(~Date_num, p = 1, q = 1, cov=TRUE),
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))


m.2<-brm(CPUE ~ poly(SalSurf_l_s, 2) + s(Temperature_s) + t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)), family=hurdle_gamma(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.9))
m.2<-add_criterion(m.2, c("loo", "waic"))

m.3<-brm(CPUE ~ poly(SalSurf_l_s, 2) + s(Temperature_s) + t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, bs="cc"), family=hurdle_gamma(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.9))
m.3<-add_criterion(m.3, c("loo", "waic"))

m4.3<-brm(CPUE ~ poly(SalSurf_l_s, 2) + s(Temperature_s) + t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, bs="cc"), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
m4.3<-add_criterion(m4.3, c("loo", "waic"))

m4.4<-brm(CPUE ~ poly(SalSurf_l_s, 2) + s(Temperature_s) + t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, Year, bs=c("cc", "cr")) + (1|Source), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
m4.4<-add_criterion(m4.4, c("loo", "waic"))

m4.5<-brm(CPUE ~ s(SalSurf_s) + s(Temperature_s) + t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, Year, bs=c("cc", "cr")) + (1|Source), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
m4.5<-add_criterion(m4.5, c("loo", "waic"))

m4.6<-brm(CPUE ~ poly(SalSurf_l_s, 3) + s(Temperature_s) + t2(Latitude_s, Longitude_s, Date_num_s, d=c(2,1)) + t2(Julian_day, Year, bs=c("cc", "cr")) + (1|Source), family=hurdle_lognormal(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control=list(adapt_delta=0.85))
m4.6<-add_criterion(m4.6, c("loo", "waic"))
save(m4.6, file="~/SDP/m4.6.RData")

m4.7<-brm(CPUE ~ poly(SalSurf_l_s, 2) + s(Temperature_s) + s(Date_num_s) + t2(Julian_day, Year, bs=c("cc", "cr")) + (1|Source) + (1|Clustered_station), family=hurdle_lognormal(),
       data=PF, cov_ranef = list(Clustered_station=distance_cov),
       prior=prior(normal(0,10), class="Intercept")+
         prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma")+
         prior(cauchy(0,1), class="sd"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control = list(max_treedepth = 15, adapt_delta=0.85))
m4.7<-add_criterion(m4.7, c("loo", "waic"))
save.image("~/SDP/CopModels.RData")

m4.8<-brm(CPUE ~ -1 + poly(SalSurf_l_s, 2) + s(Temperature_s) + s(Date_num_s) + t2(Julian_day, Year, bs=c("cc", "cr")) + (1|Source) + (1|Clustered_station), family=hurdle_lognormal(),
       data=PF, cov_ranef = list(Clustered_station=distance_cov),
       prior=prior(normal(0,5), class="b")+
         prior(cauchy(0,5), class="sigma")+
         prior(cauchy(0,1), class="sd"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup, control = list(max_treedepth = 13, adapt_delta=0.85))
m4.8<-add_criterion(m4.8, c("loo", "waic"))
save.image("~/SDP/CopModels.RData")
```

Adding normal(0,100) prior to intercept in mbase results in exact same intercept estimate

for mbaseST and mbase4ST, applying a cauchy(0,5) prior to the sds terms does not change the results. The data are too strong

```{r}
loo_compare(mbase, mbase4, mbaseST, mbase4ST, mbaseST.2, mbase4ST.2, mbaseST2, mbase4ST2, mbase4ST3, mbase4ST4, mbase4ST5, mbase4ST6, m.1, m4.1.1, m.2, m.3, m4.3, m4.4, m4.5, m4.6, m4.7, m4.8)
```


Trying poisson models on counts
```{r}
mbasecount<-brm(Count ~ Volume, family=zero_inflated_poisson(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)
mbasecount<-add_criterion(mbasecount, c("loo", "waic"))

mbasecount2<-brm(Count ~ Volume, family=zero_inflated_negbinomial(),
       data=PF,
       prior=prior(normal(0,10), class="Intercept"),
       chains=1, cores=1,
       iter = iterations, warmup = warmup)
mbasecount2<-add_criterion(mbasecount2, c("loo", "waic"))
```

posterior predictive checks
```{r}
pp <- function(model){
  prop_zero <- function(x) mean(x == 0)
  
  p<-list()
  
  p$zero<-pp_check(model, type="stat", stat=prop_zero)
  
  p$dist<-pp_check(model)+scale_x_log10()
  
  return(p)
}

```

```{r}
newdata <- expand.grid(Latitude_s=seq(min(PF$Latitude_s), max(PF$Latitude_s), length.out = 100), Longitude_s=seq(min(PF$Longitude_s), max(PF$Longitude_s), length.out = 100), Date_num_s=c(-1.633522,-0.022668713,	1.592155), Julian_day=182, SalSurf_l_s=0, Temperature_s=0)%>%
  mutate(Year = case_when(
    Date_num_s < (-1.5) ~ 1998,
    Date_num_s > (-1) & Date_num_s < 1~ 2008,
    Date_num_s > 1~ 2018
  ))%>%
  mutate(Latitude=Latitude_s*sd(PF$Latitude)+mean(PF$Latitude),
         Longitude=Longitude_s*sd(PF$Longitude)+mean(PF$Longitude))

pred<-fitted(m4.4, newdata = newdata, re_formula=NA)

newdata$CPUE<-pred[,1]
```

```{r}
p1998<-ggplot(filter(newdata, Year==1998), aes(x=Longitude, y=Latitude))+
  geom_contour_filled(aes(z=CPUE))+
  theme_bw()+
  theme(panel.grid=element_blank(), strip.background = element_rect(fill="white", color="black"), legend.position = "none")
p1998

p2008<-ggplot(filter(newdata, Year==2008), aes(x=Longitude, y=Latitude))+
  geom_contour_filled(aes(z=CPUE))+
  theme_bw()+
  theme(panel.grid=element_blank(), strip.background = element_rect(fill="white", color="black"), legend.position = "none")
p2008

p2018<-ggplot(filter(newdata, Year==2018), aes(x=Longitude, y=Latitude))+
  geom_contour_filled(aes(z=CPUE))+
  theme_bw()+
  theme(panel.grid=element_blank(), strip.background = element_rect(fill="white", color="black"), legend.position = "none")
p2018
```

